Getting start

### 2020-12-02 inst/gitbook/01_getting_started.Rmd
Update 01_getting_started.Rmd

```{r}
## Setting the simulation parameters
extinction_02 <- list(extinction = 0.4)
living_20     <- list(max.living = 20)
BM_trait      <- make.traits()
set.seed(4242)
## Simulate disparity and diversity
default_data <- dads(bd.params = extinction_02,
                     stop.rule = living_20,
                     traits    = BM_trait,
                     modifiers = default_modifiers)
default_data
```

@@

```{r}
## Triggering a modification only if the ancestor trait is negative
negative.ancestor <- function(trait.values, parent.lineage) {
    return(all(parent.traits(trait.values, parent.lineage) < 0))
}
```

@@

```{r}
set.seed(4242)
## Simulate disparity and diversity
biased_data <- dads(bd.params = extinction_02,
                    stop.rule = living_20,
                    traits    = BM_trait,
                    modifiers = negatives_extinct)
biased_data
```

>>>>

```{r}
## Setting the simulation parameters
extinction_02 <- list(extinction = 0.2)
living_20     <- list(max.living = 20)
BM_trait      <- make.traits()
set.seed(1)
## Simulate disparity and diversity
default_data <- dads(bd.params = extinction_02,
                     stop.rule = living_20,
                     traits    = BM_trait,
                     modifiers = default_modifiers)
default_data
```

@@

```{r}
## Triggering a modification only if the ancestor trait is negative
negative.ancestor <- function(trait.values, lineage) {
    return(all(parent.traits(trait.values, lineage) < 0))
}
```

@@

```{r}
set.seed(1)
## Simulate disparity and diversity
biased_data <- dads(bd.params = extinction_02,
                    stop.rule = living_20,
                    traits    = BM_trait,
                    modifiers = negatives_extinct)
biased_data
```
